---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# stylex

<!-- badges: start -->
[![Codecov test coverage](https://codecov.io/gh/jonthegeek/stylex/branch/main/graph/badge.svg)](https://codecov.io/gh/jonthegeek/stylex?branch=main)
[![R-CMD-check](https://github.com/jonthegeek/stylex/workflows/R-CMD-check/badge.svg)](https://github.com/jonthegeek/stylex/actions)
<!-- badges: end -->

Neural style transfer is the process of using the style of one  image and the content of another to produce a new image ([Gatys, Ecker,Bethge (2015) <arXiv:1508.06576>](https://arxiv.org/abs/1508.06576)). 
Implementing style transfer often involves multiple iterations to dial in the desired effect. 
This package aims to guide the user through that process.

This package was heavily inspired by a [blog by Athos Damiani](https://blog.curso-r.com/posts/2021-02-22-neural-style-transfer/).

## Installation

You can install the released version of stylex from [CRAN](https://CRAN.R-project.org) with:

``` r
# No you can't.
# install.packages("stylex")
```

And the development version from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("jonthegeek/stylex")
```
## Example

<Fill in examples here.>

```{r example}
library(stylex)
## basic example code to come
```

